Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-03 MUSES_vs_BYOD_solutions.tex
Added thesis required by referee for issue #27

%%%%FERGU-SOA
%Estoy metiendo aquí los párrafos de los nuevos papers que pide el revisor 3, no sé si esta es la mejor sección
Besides, there is an emerging research area in the field of BYOD. This is because, as it has been mentioned, it is becoming a growing trend \cite{Garba15organisational}. 
Although some works present studies on its impact in workers relationship between productivity and stress \cite{Haejung12Door}, the most of them are focused in describing new systems and concepts in this paradigm. The work \cite{Scarfo12survey} presents a survey about the coming up methods in BYOD security. This survey summarizes the research in two different approaches: {\em hands-off} versus {\em hand-on} devices. The first one proposes the use of some kind of virtualization or wrapping of the applications, while the latter is based in a tight control and monitoring of the device by the company.

>>>>

%%%%FERGU-SOA
%Estoy metiendo aquí los párrafos de los nuevos papers que pide el revisor 3, no sé si esta es la mejor sección
Besides, there is an emerging research area in the field of BYOD. This is because, as it has been mentioned, it is becoming a growing trend \cite{Garba15organisational}. There exist several methodological works on this subject. Samaras \cite{Samaras13SaaS} proposes a methodology design of a security architecture taking into account their logical design, logical architecture, security mechanisms and physical architecture. First, the business processes are studied and legal and security requirements are analysed. After applying several controls the architecture is validated using different criteria: Correctness, Completeness, Usability and Flexibility.

Although some works present studies on the impact of BYOD in workers relationship between productivity and stress \cite{Haejung12Door}, the most of them are focused in describing new systems and concepts in this paradigm. The work \cite{Scarfo12survey} presents a survey about the coming up methods in BYOD security. This survey summarizes the research in two different approaches: {\em hands-off} versus {\em hand-on} devices. The first one proposes the use of some kind of virtualization or wrapping of the applications, while the latter is based in a tight control and monitoring of the device by the company.
